---
title: "Curriculum Vitae: Cole Brokamp, Ph.D."
output:
  word_document:
    reference_docx: reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(purrr)
library(glue)
```

# Personal Data

```{r}
#| child: data/personal_data.Rmd
```

# Education

## Academic Education

```{r}
#| child: data/education.Rmd
```

## Training Courses and Workshops
- 2015: “Bayesian Methods for Clinical Trials.” A training workshop provided by Berry Consultants.
- 2017: “Intermediate R Shiny.” A pre-conference training workshop provided by R Studio at the R Studio Conference 2017.
- 2017: “Write Winning Grants.” A two-day training workshop provided by University of Cincinnati.
- 2018: “Machine Learning for Causal Inference in Environmental Health Studies.” A pre-conference training workshop provided by the International Societies of Exposure Science and Environmental Epidemiology (ISEE & ISES) at the ISEE/ISES 2018 Annual Meeting.
- 2019: “Junior Investigators Workshop.” A two-day pre-conference training workshop provided by the Biometrics Society at the Eastern Northern American Region (ENAR) at the Biometrics Society 2019 Annual Meeting.
- 2020: “Practical Solutions for Working with Electronic Health Records Data.” A one-day pre-conference training workshop provided by the Biometrics Society at the Eastern Northern American Region (ENAR) at the biometris Society 2020 Annual Meeting.
- 2020: “Causal Inference Using the R TWANG Package for Mediation and Continuous Exposures.” A tutorial provided by the Biometrics Society at the Eastern Northern American Region (ENAR) at the Biometrics Society 2020 Annual Meeting.
- 2020: “Fundamentals of Difference-in-Differences Studies.” A tutorial provided by the Biometrics Society at the Eastern Northern American Region (ENAR) at the Biometrics Society 2020 Annual Meeting.
- 2021: “Introduction to tileDB for R.” A tutorial at the useR! 2021 Annual Meeting.
- 2022: “Tidy Development Tools.” A pre-conference training workshop provided by R Studio at the R Studio Conference 2022.
- 2023: “Which Comes First: High Quality Clinical Data or Reliable AI-based Applications?” A pre-conference training workshop at the 2023 American Medical Informatics Association (AMIA) Informatics Summit.

# Academic Appointments

```{r}
#| child: data/academic_appointments.Rmd
```

# Licensing and Certification

- CITI Training  
  – 2019-07-31: Responsible Conduct of Research  
  – 2019-07-31: Human Subjects Research Core  
  – 2019-07-31: Children Research  
  – 2019-10-10: Good Clinical Practice  
  – 2019-10-10: Clinical Research Conduct  

# Awards and Honors

```{r}
#| child: data/awards_and_honors.Rmd
```

# Research and Scholarly Activities

```{r}
make_support_entry <- function(x) {
  glue::glue_data(
    x,
    "*{title}*",
    "{source} {number}, PI: {pi_name}",
    "{status}. {scales::dollar(amount)}. {start_date} - {end_date}.",
    .sep = "  \n", .na = " "
  ) 
}
```

## Research and Scholarly Activities

My main research focus has been to elucidate the effects of environmental exposures and community characteristics on the psychiatric well-being and mental health of children and adolescents. Through creating new place-based data science tools and environmental exposure methods, I have been able to both lead my own research program based on existing cohorts and the CCHMC electronic health records, as well as make methodological contributions to several different nationwide multi-site studies. 

## Grants and Contracts

### Current

```{r}
#| results: asis
yaml::yaml.load_file("data/support.yaml") |>
  purrr::keep(\(x) x$status == "Active") |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

### Selected Previous (Brokamp, PI)

```{r}
#| results: asis
yaml::yaml.load_file("data/support.yaml") |>
  purrr::keep(\(x) x$status == "Completed") |>
  purrr::keep(\(x) x$pi_name == "Brokamp C") |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

## Publications

### Peer reviewed articles
	
```{r}
#| results: asis
yaml::yaml.load_file("data/pubs.yaml") |>
  map_chr(\(x) glue_data(x,
                         "1",
                         "{paste(author, collapse = ', ')}",
                         "{title}",
                         "*{journal}*",
                         "{issue_pages}",
                         "{year}.",
                         .sep = ". ",
                         .na = character())) |>
  map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
  rev() |>
  cat(sep = "\n")
```

### Quality Review of Publications

Publications I have authored have 1,819 total citations (1,593 since 2018), with an h-index of 25 (23 since 2018), and an i10-index of 40 (40 since 2017). Below are quality reviews of seven selected publications:

1. **Cole Brokamp**, Roman Jandarov, Monir Hossain, Patrick Ryan. Predicting Daily Urban Fine Particulate Matter Concentrations Using Random Forest. Environmental Science & Technology. 52 (7). 4173-4179. 2018.  
  – I lead this publication by designing and completing all of the analyses. We used satellite data combined with weather and land use data to create a machine learning model that can accurately estimate daily exposure to ambient fine particulate matter at any location in the Greater Cincinnati Area from 2000 to the present.  
  – 116 total citations since publication on 2018-03-14 (2023:4, 2022: 34, 2021: 32, 2020: 25, 2019: 20)  

2.	**Cole Brokamp**, Chris Wolfe, Todd Lingren, John Harley, Patrick Ryan. Decentralized and Reproducible Geocoding and Characterization of Community and Environmental Exposures for Multi-Site Studies. Journal of American Medical Informatics Association. 25(3). 309-314. 2017.  
  – I lead and completed all of the software development and validation for this study which summarized our software tool that can be used to securely geocode and estimate community and environmental exposures (geomarker assessment) within multi-site studies where sharing of protected health information is not feasible.  
  – 52 total citations since publication on 2018-03-01 (2023: 3, 2022: 17, 2021: 10, 2020: 6, 2019: 11, 2018: 5)  

3.	**Cole Brokamp**, Jeffrey R. Strawn, Andrew F. Beck, Pat Ryan. Pediatric Psychiatric Emergency Department Utilization and Fine Particulate Matter: A Case-Crossover Study. Environmental Health Perspectives. 127(9). 2019. PMID: 31553231  
  – As the lead author, I designed and executed this study utilizing CCHMC electronic health records and my spatiotemporal air pollution exposure assessment model. Notably, this was the first scientific publication to show that short-term air pollution is associated with psychiatric exacerbations in children and adolescents.  
  – 36 total citations since publication on 2019-09-25 (2022: 16, 2021: 16, 2020: 4)  
  – Selected as the top publication and top research achievement of 2020 for the Division of Biostatistics and Epidemiology and featured in the Cincinnati Children’s 2020 Annual Research Report  
  – Featured in several high-profile media outlets, including Newsweek, CNN, The London Time, Forbes, and over 30 other outlets  

4.	**Cole Brokamp**, Roman Jandarov, MB Rao, Grace LeMasters, Patrick Ryan. Exposure assessment models for elemental components of particulate matter in an urban environment: A comparison of regression and random forest approaches. Atmospheric Environment. 151. 1-11. 2017.  
  – I lead and completed all analyses for this study that was the first to utilize the machine learning method, random forest, to predict airborne concentrations of twelve different components of fine particulate matter air pollution. We showed that the random forest method outperformed traditional regression methods. The resulting exposure assessment models can be used to estimate air pollution exposures at any specific address in the seven counties surrounding Cincinnati, OH.  
  – 174 total citations since publication on 2017-02-01 (2023: 4, 2022: 45, 2021: 33, 2020: 30, 2019: 26, 2018: 28, 2017: 10)  
  – Selected as the top publication of 2017 for the Division of Biostatistics and Epidemiology and featured in the Cincinnati Children’s 2017 Annual Research Report  

5.	**Cole Brokamp**, Grace LeMasters, Patrick Ryan. Residential mobility impacts exposure assessment and community socioeconomic characteristics in longitudinal epidemiology studies. Journal of Exposure Science and Environmental Epidemiology. 26(4). 428-34. 2016.  
  – As the lead author, I completed all analyses for this manuscript which showed that ignoring unknown residential location changes in longitudinal epidemiology studies leads to bias in health outcome studies.  
  – 60 total citations since publication on 2016-06-01 (2022: 13, 2021: 9, 2020: 12, 2019: 13, 2018: 8, 2017: 3)  

6.	**Cole Brokamp**, Andrew F Beck, Neera K Goyal, Patrick Ryan, James M Greenberg, Eric S Hall. Material community deprivation and hospital utilization during the first year of life: an urban population-based cohort study. Annals of Epidemiology. 30. 37-43. 2019.  
  – As the primary author, I designed and completed all analyses for this manuscript which created a community material deprivation index and used a causal inference framework to show that community poverty causes increased healthcare utilization in newborns independently of their individual-level socioeconomic status and race. The created nationwide deprivation index has been used as a resource in numerous other publications and public health applications.  
  – 80 total citations since publication on 2019-02-01 (2023:  3, 2022: 33, 2021: 24, 2020: 18, 2019: 2)  

7.	Juliana Madzia, Patrick Ryan, Kimberly Yolton, Zana Percy, Nick Newman, Grace LeMasters, **Cole Brokamp**. Residential greenspace is associated with childhood behavioral outcomes. The Journal of Pediatrics. 207. 233-240. 2019.  
  – As the senior author, I designed and oversaw all analyses for this manuscript, including the work completed by my mentee, who was the first author. We used a cohort of Cincinnati children to show that increased greenspace around their residences was associated with reduced problems related to misconduct, anxiety, and depression.  
  – 46 total citations since publication on 2019-04-01 (2023: 2, 2022: 23, 2021: 15, 2020: 6)  

## Patents

1.	Assem Ziady, Rhonda Szczesniak, John Clancy, **Cole Brokamp**, inventors; Cincinnati Children’s Hospital Medical Center, assignee. Compositions and methods for treatment of lung function. United States patent US 10,761,099. 2020 Sep 1.

## Selected Abstracts (First or Senior Author)

\* denotes the presenting author

```{r echo = FALSE, results = 'asis'}
yaml::yaml.load_file("data/abstracts.yaml") |>
  map_chr(\(x) glue_data(x,
                         "1",
                         "{paste(author, collapse = ', ')}",
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}.",
                         .sep = ". ",
                         .na = character())) |>
  map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
  rev() |>
  cat(sep = "\n")
```

# Teaching and Mentoring

## Invited Lectures

```{r echo = FALSE, results = 'asis'}
yaml::yaml.load_file("data/talks.yaml") |>
  purrr::keep(\(.) pluck(., "type") == "invited") |>
  map_chr(\(x) glue_data(x,
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}",
                         .sep = ". ",
                         .na = character())) |>
  cat(sep = "\n\n")
```

## Seminars

```{r echo = FALSE, results = 'asis'}
yaml::yaml.load_file("data/talks.yaml") |>
  purrr::keep(\(.) pluck(., "type") == "seminar") |>
  map_chr(\(x) glue_data(x,
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}",
                         .sep = ". ",
                         .na = character())) |>
  cat(sep = "\n\n")
```

## Teaching

```{r echo = FALSE, results = 'asis'}
yaml::yaml.load_file("data/talks.yaml") |>
  purrr::keep(\(.) pluck(., "type") == "teaching") |>
  map_chr(\(x) glue_data(x,
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}",
                         .sep = ". ",
                         .na = character())) |>
  cat(sep = "\n\n")
```

## Mentoring

#### Undergraduate Students

- Amisha Saini, CCHMC Summer Undergraduate Research Fellowship: Primary Mentor (2021, 2022)
- Milan Parikh, UC College of Medicine: Primary Research Mentor (2021 - 2023)
- Daniel Ehrlich, Undergraduate Research Assistant (2018 - 2019)

#### MS Students

- Erika Rasnick, Miami of Ohio Statistics: Thesis committee member (2018 - 2019)
- Yajna Jathan, UC College of Engineering: Thesis committee member (2019 - 2020)
- Clayton Peterson: UC College of Medicine Biostatistics: Thesis committee member (2021 - 2022)
- Madhumitaa Roy, UC College of Engineering: Thesis committee member (2020 - 2021)

#### PhD or MD Students

- Madhumitaa Roy, UC College of Engineering: Dissertation committee member (2021 - 2023)
- Harsimran Makkad: CCHMC Summer Medical Student Respiratory Research Fellowship: Primary Mentor (2023)
- Stephen Colegate: UC College of Medicine Biostatistics: Dissertation committee member (2020 - 2022)
- Ziyun Wang: UC College of Medicine Biostatistics: Dissertation committee member (2022 - 2023)
- Kacey Apple: UC College of Medicine Epidemiology: Dissertation committee member (2018 - 2022)
- Jordan Pennington, CCHMC Summer Medical Student Respiratory Research Fellowship: Primary Mentor (2020)
- Ashley Turner: UC College of Medicine Industrial Hygiene: Dissertation committee member (2020 - 2021)
- Shannon Conrey: UC College Of Medicine Epidemiology: Dissertation committee member (2019 - 2021)
- Mohammad Alfrad Nobel Bhuiyan, UC College of Medicine Biostatistics: Research Mentor (2018-2019)
- Lei Liu, UC College of Medicine Biomedical Informatics: Dissertation committee member (2019 - 2021)
- Kim Hartley, UC College of Medicine Nursing: Dissertation committee member (2019 - 2020)
- Zana Percy, UC College of Medicine Medical Scientist Training Program: Qualifying exam committee member (2018 - 2019)
- Juliana Madzia, UC College of Medicine Medical Scientist Training Program: PhD dissertation committee co-chair (2018 - 2020)

#### Post Graduate Clinical and Research Fellows

- Clara Zundel, Wayne State University Research Fellow: Member of F32 Mentorship Committee (2022 - present)
- Anushka Palipana, CCHMC Research Fellow: Member of Career Development Committee (2022 - 2023)
- Stephen Colegate, CCHMC Research Fellow: Chair of Career Development Committee and Primary Research Mentor (2022 – present)
- Kim Hartley, CCHMC General Pediatric Research Fellowship: Scholarship Overshight Committee (2020 - 2023)
- Sharad Wadhwani, CCHMC Clinical Research Fellow: Research mentor (2017 - 2019)
- Emrah Gecili, CCHMC Postdoctoral Research Fellow: Career development committee (2019 - 2022)
- Adam Jasne, UC College of Medicine Stroke Research Fellow: Research mentor (2016 - 2018)
- Anh Dao: UC College of Medicine Division of Immunology, Allergy and Rheumatology: T32 Research Fellow Oversight Committee (2017 - 2019)
- Kristy Schmidlin: UC College of Medicine Division of Immunology, Allergy and Rheumatology: T32 Research Fellow Oversight Committee (2016 - 2017)
- Jennifer Kannan: UC College of Medicine Division of Immunology, Allergy and Rheumatology: T32 Research Fellow Oversight Committee (2016 - 2017)
- Jessica Tan: UC College of Medicine Division of Immunology, Allergy and Rheumatology: T32 Research Fellow Oversight Committee (2016 - 2017)

#### K/Training Award Mentees

- Anita Shaw, UC College of Medicine: Research mentor committee member for PEDSnet KL2 Training Award (2018 - 2020)
- Meera Kotagal, UC College of Medicine: Research mentor committee member for CCTST KL2 Training Award (2023 - 2024)

# Service and Leadership

```{r}
#| child: data/service_and_leadership.Rmd
```

# Distribution of Effort

|Activity|Percent Effort|
|-------:|:-------------|
|Research and Scholarly Activities | 90%
|Teaching and Mentoring | 5%
|Service and Leadership | 5%
|Clinical Service | 0%

I have reviewed the curriculum vita for completeness and accuracy and agree with its contents.

Division Director Signature and Date:

Faculty Member Signature and Date:

Date of Preparation: `r Sys.Date()`
