---
title: "Curriculum Vitae: Cole Brokamp, Ph.D."
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r}
library(dplyr)
library(purrr)
library(glue)
```

# Personal Data

```{r}
#| child: data/personal_data.Rmd
```

# Research Interests

- Place-based data science
- Environmental epidemiology
- Population health
- Causal inference machine learning methods
- Fairness in precision medicine

# Education

```{r}
#| child: data/education.Rmd
```

# Academic Appointments

```{r}
#| child: data/academic_appointments.Rmd
```

# Grants and Contracts

```{r}
make_support_entry <- function(x) {
  glue::glue_data(
    x,
    "*{title}*",
    "{source} {number}, PI: {pi_name}",
    "{status}. {scales::dollar(amount)}. {start_date} - {end_date}.",
    .sep = "  \n", .na = " "
  ) 
}
```

### Current

```{r}
#| results: asis
yaml::yaml.load_file("data/support.yaml") |>
  purrr::keep(\(x) x$status == "Active") |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

<!-- ### Pending (Brokamp, PI) -->

<!-- ```{r} -->
<!-- #| results: asis -->
<!-- yaml::yaml.load_file("data/support.yaml") |> -->
<!--   purrr::keep(\(x) x$status == "Pending") |> -->
<!--   purrr::keep(\(x) x$pi_name == "Brokamp C") |> -->
<!--   purrr::map_chr(make_support_entry) |> -->
<!--   cat(sep = "\n\n") -->
<!-- ``` -->

### Selected Previous (Brokamp, PI)

```{r}
#| results: asis
yaml::yaml.load_file("data/support.yaml") |>
  purrr::keep(\(x) x$status == "Completed") |>
  purrr::keep(\(x) x$pi_name == "Brokamp C") |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

# Publications

```{r}
#| results: asis
yaml::yaml.load_file("data/pubs.yaml") |>
  map_chr(\(x) glue_data(x,
                         "{paste(author, collapse = ', ')}",
                         "{title}",
                         "*{journal}*",
                         "{issue_pages}",
                         "{year}.",
                         .sep = ". ",
                         .na = character())) |>
  map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
  cat(sep = "\n\n")
```

## Selected Abstracts (First or Senior Author)

\* denotes the presenting author

```{r}
#| results: asis
yaml::yaml.load_file("data/abstracts.yaml") |>
  map_chr(\(x) glue_data(x,
                         "{paste(author, collapse = ', ')}",
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}.",
                         .sep = ". ",
                         .na = character())) |>
  map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
  cat(sep = "\n\n")
```

# Talks

```{r echo = FALSE, results = 'asis'}
yaml::yaml.load_file("data/talks.yaml") |>
  map_chr(\(x) glue_data(x,
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}",
                         .sep = ". ",
                         .na = character())) |>
  cat(sep = "\n\n")
```

# Awards and Honors

```{r}
#| child: data/awards_and_honors.Rmd
```

# Service and Leadership

```{r}
#| child: data/service_and_leadership.Rmd
```

\vfill

Last Updated: `r Sys.Date()`
