---
title: ""
output:
  pdf_document:
    includes:
      in_header: "_nih_bio_styles.tex"
    latex_engine: xelatex
linestretch: 1.0
fontsize: 11pt
mainfont: Arial
indent: false
pagestyle: empty
geometry:
- left=0.5in
- right=0.5in
- top=0.5in
- bottom=0.5in
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
d <- yaml::read_yaml("data/biosketch.yaml")
## download.file("https://grants.nih.gov/grants/forms/biosketch-blank-format-rev-10-2021.docx",
              ## "biosketch-blank-format-rev-10-2021.docx")
```

\setlength{\parskip}{0pt}
\pgline\centerline{\textbf{BIOGRAPHICAL SKETCH}}

\footnotesize
\centerline{Provide the following information for the Senior/key personnel and other significant contributors.}

\centerline{Follow this format for each person.  \textbf{DO NOT EXCEED FIVE PAGES}}

\normalsize

\pgline NAME: `r glue::glue_data(d, "{name}")`

\pgline eRA COMMONS USER NAME (credential, e.g., agency login): `r glue::glue_data(d, "{era_commons_name}")`

\pgline POSITION TITLE: `r glue::glue_data(d, "{position_title}")`

\pgline EDUCATION/TRAINING (\textit{Begin with baccalaureate or other initial professional education, such as nursing, include postdoctoral training and residency training if applicable. Add/delete rows as necessary.})

&nbsp;

\renewcommand{\arraystretch}{1.7}

```{r}
d$education_and_training |>
  purrr::map(tibble::as_tibble) |>
  purrr::list_rbind() |>
  tidyr::unite(inst_loc, institution, location, sep = "; ") |>
  knitr::kable(col.names = c("INSTITUTION AND LOCATION",
                             "DEGREE (if applicable)",
                             "Completion Date MM/YYYY",
                             "FIELD OF STUDY"),
               bottomrule = "",
               linesep = "",
               position = "h!",
               format = "latex") |>
  kableExtra::column_spec(1, width = "3.5in") |>
  kableExtra::column_spec(2, width = "0.8in") |>
  kableExtra::column_spec(3, width = "1in") |>
  kableExtra::column_spec(4, width = "1.6in" ) |>
  kableExtra::row_spec(0, align = "c") |>
  kableExtra::row_spec(1:99, align = "l")
```

\renewcommand{\arraystretch}{1}

```{r}
# function that takes in a vector of **four** (or less) identifers from pubs.yaml and inserts the citations in that order

cite_four <- function(.x = c("rasnick-2023", "pennington-2022", "vancil-2022")) {
  stopifnot(length(.x) <= 4)
  pubs <- yaml::yaml.load_file("data/pubs.yaml")
  stopifnot(all(.x %in% names(pubs)))
  the_pubs <- purrr::map(.x, \(.) purrr::pluck(pubs, .))
  the_pubs |>
    purrr::map_chr(\(.) glue::glue_data(.,
                           "1",
                           "{paste(author, collapse = ', ')}",
                           "{title}",
                           "*{journal}*",
                           "{issue_pages}",
                           "{year}.",
                           .sep = ". ",
                           .na = character())) |>
    purrr::map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
    cat(sep = "\n\n")
}

make_support_entry <- function(x) {
  glue::glue_data(
    x,
    "{source} {number}",
    "{pi_name} (PI)",
    "{start_date} - {end_date}",
    "*{title}*",
    .sep = "  \n", .na = " "
  ) 
}
```

\setlength{\parskip}{6pt}

# A. Personal Statement

As a biostatistician, epidemiologist, and geospatial data scientist, I have specialized myself in the areas of informatics and machine learning with applications to large environmental, community, and health outcome datasets. Recent democratization of “big spatial data” and advances in geoinformatics have allowed unprecedented access to environmental and socioeconomic characteristics that vary highly with respect to both time and space. More precise environmental features require more complex modeling and I have dedicated my early career to furthering exposure science methodology in order to bring more precise exposure assessment tools to environmental and population health studies. This includes high resolution spatiotemporal exposure assessment models for fine particulate matter as well as a longitudinal measure of material community deprivation. Furthermore, I have developed a novel approach and accompanying software package called DeGAUSS which allows for user-friendly attachment of geospatial variables to existing research cohorts while mitigating key privacy challenges. I am the founding director of the Geospatial Research Accelerator for Precision Population Health (GRAPPH), which is a shared facility at Cincinnati Children’s Hospital Medical Center that works to develop and democratize geospatial data and methodologies across the institution.

Leveraging these advanced exposure assessment models, I’ve lead epidemiologic studies demonstrating the roles of air pollution, greenspace, and poverty on psychiatric and neurobehavioral child health outcomes. Furthermore, I co-lead health equity research with investigators who are seeking to quantify and identify causal drivers of racial and ethnic health disparities. My research also extends into the racial and ethnic fairness of precision health algorithms, including applications within asthma, cystic fibrosis, and assessment of socioeconomic status and environmental exposures.

Ongoing projects I would like to highlight include:

```{r}
#| results: asis
yaml::yaml.load_file("data/support.yaml") |>
  purrr::keep_at(c("tes-r01", "degauss-r01", "beck-riseup", "nancy-r01", "c4", "brunst-epigenetics")) |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

Citations:

```{r}
#| results: asis
cite_four(c("rasnick-2023", "vancil-2022", "pennington-2022", "brokamp-2024"))
```

# B. Positions, Scientific Appointments, and Honors

## Positions and Scientific Appointments

```{r}
d$positions |>
  purrr::map(tibble::as_tibble) |>
  purrr::list_rbind() |>
  tidyr::unite(title_inst, title, institution, sep = ", ") |>
  knitr::kable(col.names = NULL,
               toprule = "",
               linesep = "",
               bottomrule = "",
               position = "h!") |>
  kableExtra::column_spec(1, width = "0.9in") |>
  kableExtra::column_spec(2, width = "6.2in") |>
  kableExtra::row_spec(0:99, align = "l")
```

## Honors

```{r}
d$honors |>
  purrr::map(tibble::as_tibble) |>
  purrr::list_rbind() |>
  knitr::kable(col.names = NULL,
               toprule = "",
               linesep = "",
               bottomrule = "",
               position = "h!") |>
  kableExtra::column_spec(1, width = "0.9in") |>
  kableExtra::column_spec(2, width = "6.2in") |>
  kableExtra::row_spec(0:99, align = "l")
```

# C. Contributions to Science

## Spatiotemporal exposure assessment methods and machine learning models

My early career was spent developing spatiotemporal exposure assessment models for environmental pollutants and community characteristics based on machine learning techniques.  This work includes the first machine learning or ensemble model used to assess exposure to elemental components of particulate matter. Recent introduction of remote sensing satellite data has allowed for extension of the land use random forest model to produce daily estimates of air pollution back to 2000 at a resolution of 1 x 1 km. 

```{r}
#| results: asis
cite_four(c("brokamp-2022", "brokamp-2019a", "brokamp-2018", "brokamp-2017"))
```

## Community Material Deprivation Index

I created a nationwide, census tract-level, and validated community material deprivation index that has been used and cited by over 75 different published scientific studies. It was originally created to estimate the causal impact of community material deprivation on hospitalization during the first year of life, but has also been used across several medical subspecialties to quantify health disparities. Additionally, I recently co-mentored a fellow to publish a scoping review and set of recommendations for the use of area based socioeconomic deprivation indices.

```{r}
#| results: asis
cite_four(c("brokamp-2019", "trinidad-2022", "trinidad-2022b", "brokamp-2024"))
```

## Built Environment and Pediatric Psychiatric Disorders

Building on advanced exposure assessment has allowed me to lead epidemiological studies on the impacts of the built environment (e.g., fine particulate matter, greenspace, community deprivation) on psychiatric and neurobehavioral pediatric health outcomes. I lead the first study to associate fine particulate matter with psychiatric outcomes in children and adolescents, using both electronic health record studies, as well as smaller, longitudinal panel studies.
  
```{r}
#| results: asis
cite_four(c("vancil-2022", "zundel-2022", "rasnick-2021", "brokamp-2019b"))
# zundel-2022
```

## Causal Mediation of Place-Based Factors on Health Disparities

I have used advanced causal modeling techniques coupled with population-wide health registries linked to extant social and environmental determinants of health data sources to study the mechanisms behind racial health disparities. This has included neighborhood-level drivers of all-cause hospitalization disparities and more detailed analyses within specific disease groups, including pediatric inflammatory bowel disease, asthma, sickle cell anemia, type I diabetes, and psychiatric disorders. 

```{r}
#| results: asis
cite_four(c("brokamp-2024", "smith-2023", "esteban-2022", "zanobetti-2022"))
```
  
## Privacy-based Methods and Software for Geocoding and Geomarker Assessment

I have developed a novel approach and accompanying software package called DeGAUSS which overcomes multiple privacy-related challenges in the use of address data in multi-site studies and also serves as a more general reproducible and scalable research tool for geocoding and geomarker assessment. This approach is currently being implemented in a wide variety of national environmental health studies. Extending this approach into a scalable and sustainable framework for automated integration of disparate and heterogeneous geomarkers via spatiotemporal location has reduced the need for manual data curation and specialized expertise required to utilize them within biomedical research studies.

```{r}
#| results: asis
cite_four(c("rasnick-2023", "ryan-2020", "brokamp-2018a", "brokamp-2017b"))
```

<!-- ## Fairness in Precision Medicine -->

<!-- ```{r} -->
<!-- #| results: asis -->
<!-- cite_four(c("pennington-2022")) -->
<!-- ``` -->

**Complete list of published work in ORCID**:

[https://orcid.org/0000-0002-0289-3151](https://orcid.org/0000-0002-0289-3151)


