---
title: "Curriculum Vitae: Cole Brokamp, Ph.D."
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r}
library(dplyr)
library(purrr)
library(glue)
```

# Personal Data

- Name: Richard "Cole" Brokamp, Ph.D.
- Position: Associate Professor, University of Cincinnati College of Medicine
- Mailing Address:
    Division of Biostatistics and Epidemiology
    Cincinnati Children’s Hospital Medical Center
    3333 Burnet Avenue, MLC 5041
    Cincinnati, OH 45229-3039
- Phone: (513) 517-0289
- Fax: (513) 636-7509
- Email: cole.brokamp@cchmc.org
- Homepage: https://colebrokamp.com
- ORCID: [0000-0002-0289-3151](https://orcid.org/0000-0002-0289-3151)

# Research Interests

- Place-based data science
- Environmental epidemiology
- Population health
- Causal inference machine learning methods
- Fairness in precision medicine

# Education

**Cincinnati Children’s Hospital Medical Center**, Cincinnati, Ohio USA  
Postdoctoral Research Fellow, Division of Biostatistics & Epidemiology, 2016 - 2017  
Advisor: Dr. Patrick Ryan

**University of Cincinnati College of Medicine**, Cincinnati, Ohio USA
Ph.D., Department of Environmental Health, Division of Biostatistics and Bioinformatics, 2016
Advisor: Dr. M.B. Rao

**University of Cincinnati**, Cincinnati, Ohio USA
B.S., Biomedical Engineering, 2010

# Academic Appointments

- November 2017 - October 2020: Non-Tenure Track Research Assistant Professor, University of Cincinnati College of Medicine Department of Pediatrics
- November 2020 – June 2022: Tenure Track Assistant Professor, University of Cincinnati College of Medicine Department of Pediatrics
- July 2022 – present: Tenure Track Associate Professor, University of Cincinnati College of Medicine Department of Pediatrics

# Grants and Contracts

### Current

### Selected Previous (Brokamp, PI)

# Publications

```{r, echo = FALSE, results = 'asis'}
yaml::yaml.load_file("pubs.yaml") |>
  map_chr(\(x) glue_data(x,
                         "{paste(author, collapse = ', ')}",
                         "{title}",
                         "*{journal}*",
                         "{issue_pages}",
                         "{year}.",
                         .sep = ". ",
                         .na = character())) |>
  map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
  cat(sep = "\n\n")
```

# Patents

Assem Ziady, Rhonda Szczesniak, John Clancy, **Cole Brokamp**, inventors; Cincinnati Children’s Hospital Medical Center, assignee. Compositions and methods for treatment of lung function. United States patent US 10,761,099. 2020 Sep 1.

# Talks

```{r echo = FALSE, results = 'asis'}
yaml::yaml.load_file("talks.yaml") |>
  map_chr(\(x) glue_data(x,
                         "{title}",
                         "*{event}*",
                         "{location}",
                         "{year}",
                         .sep = ". ",
                         .na = character())) |>
  cat(sep = "\n\n")
```

# Awards and Honors

- 2020: CCHMC Division of Biostatistics & Epidemiology Top Research Achievement
- 2020: CCHMC Division of Biostatistics & Epidemiology Top Publication
- 2017: CCHMC Division of Biostatistics & Epidemiology Top Research Achievement
- 2017: CCHMC Division of Biostatistics & Epidemiology Top Publication
- 2016: CCHMC Division of Biostatistics & Epidemiology Travel Award
- 2016: CCHMC Arnold W. Strauss Fellowship Award
- 2015: Choose Ohio First Scholarship Recipient

# Service and Leadership

## Service

### Professional Societies

- 2014 - present: Member, International Society of Exposure Science
- 2018 - present: Member, International Society of Environmental Epidemiology
- itutional Committees
- 2023 - present: Member CCHMC Biomedical Informatics Faculty Search Committee
- 2022 - present: Member, CCHMC Artificial Intelligence Governance Council
- 2019 - present: Member, CCHMC DBE Faculty Career Development Committee
- 2022: Chair, CCHMC DBE Strategic Plan Steering Committee
- 2017 - present: Member, CCHMC DBE Strategic Plan Steering Committee
- 2017 - present: Member, CCHMC DBE Research Committee
- erence Leadership
- 2016: Chair of the Land Use Regression Modeling Session, International Society of Exposure Science Annual Meeting
- 2017: Chair of the Ensemble Learning for Air Pollution Exposure Assessment Session, International Society of Exposure Science Annual Meeting
- 2021: Chair of the Harnessing Big Data in Exposure Science Session, International Society of Exposure Science Annual Meeting
- 2021: Chair of the Environmental Exposures and Mental Health Session, International Society of Environmental Epidemiology

### Scientific Reviewer

- Journal Reviewer (12 manuscripts reviewed per year, on average):
  - Academic Pediatrics
  - American Journal of Respiratory and Critical Care Medicine
  - Annals of Epidemiology
  - Environmental Health Perspectives
  - Environment International
  - Environmental Modeling & Assessment
  - Environmental Pollution
  - Environmental Research
  - Environmental Science & Technology
  - Environmental Science & Technology Letters
  - Health & Place
  - International Journal of Environmental Research and Public Health
  - International Journal of Epidemiology
  - Journal of Exposure Science and Environmental Epidemiology
  - Journal of Open Source Software
  - PLOS ONE
  - Pediatrics
  - Stochastic Environmental Research and Risk Assessment
  - Science of the Total Environment
- Grant Reviewer:
  - 2017: Puerto Rico Science, Technology & Research Trust
  - 2018 - 2021: Arnold S. Strauss Fellowship Award, CCHMC
  - 2018 – 2020, 2022: University of Rochester Processes and Methods Grant
  - October 2019: NIH SIEE Study Section, Early Career Reviewer
  - 2020: University of Michigan M-LEEaD Center Pilot Projects
  - 2020: Ohio State University CCTS Pilot Projects
  - 2021: University of Louisville CCTS Pilot Translational & Clinical Studies Program
  - March 2022: NIH NIEHS ZES1 LKB-S (KS) Special Emphasis Panel
  - March 2022: NIH NIEHS ZES1 LWF-S (K9) Special Emphasis Panel
  - November 2022: NIH NIEHS ZES1 WL-W (K) Special Emphasis Panel
  - February 2023: NIH NCI ZCTA1 TCRB-J (M2) R Review Panel
- Abstract Reviewer:
  - 2018, 2019, 2022: International Societies of Exposure Science 
  - 2018, 2020, 2022: International Society of Environmental Epidemiology Meeting
  - 2021, 2022, 2023: American Medical Informatics Association Clinical Informatics Conference

## Leadership

- 2017 - present: Founding Director of the Geospatial Research Accelerator for Precision Population Health (GRAPPH) within the Data Management and Analysis Center at Cincinnati Children’s
- 2019 - present: Founding Leader of Cincinnati Children’s R Users Group (CCHMC RUG)

\vfill

Last Updated: `r Sys.Date()`
