\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

% list1 is small indent
% list2 is big indent
% list3 is no indent

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.4in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0in}}}{\end{list}}

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\begin{document}

\name{Cole Brokamp \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}      
Division of Biostatistics and Epidemiology & {\it Voice:}  (513) 518-5121 \\         
Cincinnati Children's Hospital Medical Center & {\it E-mail:}  cole.brokamp@gmail.com\\       
Cincinnati, OH 45229 USA  & {\it Website:} www.colebrokamp.com \\     
\end{tabular}


\section{\sc Research Interests}
Machine learning applied to biomedical data, statistical methods for random forest,
statistical computing, environmental health, air pollution, land use modeling

\section{\sc Education}

{\bf Cincinnati Children's Hospital Medical Center}, Cincinnati, Ohio USA \\
\vspace*{-.1in}
\begin{list1}
    \item[]Postdoctoral Research Fellow, April 2016 -- present
\end{list1}

{\bf University of Cincinnati}, Cincinnati, Ohio USA \\
\vspace*{-.1in}
\begin{list1}
\item[]Ph.D., Biostatistics, April 2016
\end{list1}

{\bf University of Cincinnati}, Cincinnati, Ohio USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[]B.S., Biomedical Engineering,  June 2010
\end{list1}


\section{\sc Research Experience}

\textbf{Department of Biostatistics and Epidemiology, Cincinnati Children's Hospital Medical Center} \\

\vspace{-0.2in}

\textsl{Spatiotemporal Land Use Models}
\hfill \textit{April 2016 -- present} \\
Advisor: Patrick Ryan, Roman Jandarov\\
\vspace{-0.13in}
\begin{list1}
    \item[]Develop spatiotemporal land use model use for elemental components of particulate matter based on land use and satellite date.
\end{list1}

\textsl{Community Health}
\hfill \textit{April 2016 -- present} \\
Advisor: Andrew Beck\\
\vspace{-0.13in}
\begin{list1}
    \item[]Contributing GIS and statistical tools to a community-centered action plan to improve the health of children in the local Avondale community.
\end{list1}


\textsl{Offline Geocoding}
\hfill \textit{April 2016 -- present} \\
Advisor: Keith Marsolo\\
\vspace{-0.13in}
\begin{list1}
    \item[]Create a nationwide geocoding program for use offline with private health information.  Incorporate local data surrounding the medical center for more accurate geocoding at the local scale. Implement as intranet application for institution wide use.
\end{list1}

\textsl{Catalyzing Ambulatory Research in Pneumonia Etiology and Diagnostic Innovations in Emergency Medicine (CARPE DIEM)}
\hfill \textit{April 2016 -- present} \\
Advisor: Lilliam Abroggio, Todd Florin\\
\vspace{-0.13in}
\begin{list1}
    \item[]Use machine learning algorithms to develop a diagnostic test to differentiate viral from bacterial community-acquired pneumonia based on metabolomics data.
\end{list1}


\textbf{Department of Biostatistics and Bioinformatics, University of Cincinnati} \\

\vspace{-0.2in}

\textsl{Statistical Inference for Random Forest}
\hfill \textit{January 2015 -- March 2016} \\
Advisor: Roman Jandarov, MB Rao \\
\vspace{-0.13in}
\begin{list1}
\item[]Deveopment of theory for calculating confidence intervals for random forest predictions using the infinitesimal jackknife.  Executed simulations to test the accuracy and precision of novel estimators.  Created software package for R to implement novel techniques to help users extract more statistical inferences from random forests.
\end{list1}

\textsl{Land Use Random Forest Model}
\hfill \textit{January 2015 -- March 2016} \\
Advisor: Roman Jandarov, MB Rao \\
\vspace{-0.13in}
\begin{list1}
    \item[]Created a novel random forest land use (LURF) model for assessing exposure to elemental components of particulate matter in the urban Cincinnati, OH area.  Showed that LURF was a more precise and accurate tool compared to land use regression. Furthermore, used tool to relate air pollution exposures to respiratory and mental health outcomes in the CCAAPS cohort.
\end{list1}


\textsl{Cincinnati Childhood Allergy and Air Pollution Study (CCAAPS)}
\hfill \textit{March 2014 -- March 2016} \\
Advisor: Patrick Ryan \\
\vspace{-0.13in}
\begin{list1}
\item[]Conducted unsupervised clustering analysis of asthmatic children into clinically-useful subtypes and machine learning based prediction of disease phenotypes. Analyzed and visualized big air pollution data from real-time, GPS equipped sensors using GIS tools. General statistical consulting for epidemiologists and clinicians involved with study. 
\end{list1}


\textsl{Relationship of Indoor Outdoor and Personal Air  (RIOPA)}
\hfill \textit{January 2014 -- November 2014} \\
Advisor: Patrick Ryan, MB Rao \\
\vspace{-0.13in}
\begin{list1}
\item[] Characterized and analyzed multivariate data using clustering and principal component techniques. Implemented machine learning algorithm for prediction of personal exposure to individual elements in PM2.5 based on indoor and outdoor air data, as well as information about potential PM2.5 sources and personal activties.
\end{list1}



\textsl{Brief Rating of Aggression by Children and Adolescents (BRACHA)}
\hfill \textit{March 2013 -- August 2014} \\
Advisor: Jeff Welge, Doug Mossman, Drew Barzman \\
\vspace{-0.13in}
\begin{list1}
\item[] Created novel data tool combining machine learning and logistic regression to predict presence, severity, frequency, and timing of aggressive acts committed in Cincinnati Children's College Hill Psychiatric Residential Clinic.
\end{list1}

 
\textbf{Department of Pharmacology and Biophysics, University of Cincinnati} \\

\vspace{-0.2in}
\textsl{Ultrasound- and Liposome-Mediated Targeted Gene Therapy}
\hfill \textit{July 2010 -- January 2012} \\
Advisor: Keith Jones, Christy Holland \\
\vspace{-0.13in}
\begin{list1}
\item[] Developed novel methodology for delivering genetic material to myocardium in mouse model of acute myocardial infarction. Ultrasound-mediated delivery of oligonucleotides targeted to suppress inflammation-related gene expression with spatial and temporal control over dosing.
\end{list1}


\textbf{Department of Biomedical Engineering, University of Cincinnati}\\

\vspace{-0.2in}
\textsl{Ion Channel Engineering and Characterization}
\hfill \textit{March 2007 -- July 2010} \\ 
Advisor: David Wendell, Carlo Montemagno \\
\vspace{-0.13in}
\begin{list1}
\item[] Implemented a planar artificial lipid bilayer system to study voltage-responsive ion currents through several ion channels. Characterized Connexin-43 and several mutants' responses to voltage differences as well as several compounds. Designed and purified several membrane proteins: genetic design and construction, protein production and purification, reconstitution into liposomes and polysomes.
\end{list1}

\section{\sc Academic Experience}
{\bf University of Cincinnati}, Cincinnati, Ohio USA

{\em Instructor} \hfill \textit{August - December, 2015}\\
Co-taught graduate level course for the Department of Biostatistics and Epidemiology.  Shared responsibility for lectures, exams,
homework assignments, and  grades.  
\vspace*{.05in}  
\begin{list2}
\item BE-9063 Computing with R Shiny, Fall 2015.
\end{list2}



\section{\sc Publications}
\input{pubs}

\section{\sc Consulting}

\textsl{Sewer Overflow} \\
Collaborators:  Louis Muglia, Andrew Beck, Patrick Ryan, Todd Trabert\\
\vspace{-0.13in}
\begin{list1}
\item[] GIS data extraction and statistical modeling for relationship between sewer overflows and admission to CCHMC.  A collaboration with the Metropolitan Sewer District of Greater Cincinnati.
\end{list1}

\textsl{Abusive Head Trauma Incidence} \\
Collaborators:  Emily Eismann, Kathi Makoroff\\
\vspace{-0.13in}
\begin{list1}
\item[] Mapping and statistical models for relationship of abusive head trauma cases at CCHMC and socioeconomic status.
\end{list1}

\textsl{Phenotypic Subtypes of Autism based on Gene Expression} \\
Collaborators:  Ping-I (Daniel) Lin\\
\vspace{-0.13in}
\begin{list1}
\item[] Semi-supervised principal components analysis on genome wide expression data and association of functional gene pathways with autistic severity scores.
\end{list1}


\textsl{Breast Density and Air Pollution} \\
Collaborators:  Lusine Yaghjyan, Patrick Ryan\\
\vspace{-0.13in}
\begin{list1}
\item[] Air pollution exposure assessment for nationwide cohort of breast cancer patients.  Model uses EPA's hierarchical Bayesian model and combines monitoring data with output from the Community Multi-scale Air Quality model.
\end{list1}

\textsl{Infectious Diseases and Trauma Transportation} \\
Collaborators:  Monir Hossain\\
\vspace{-0.13in}
\begin{list1}
\item[] Calculation of tranportation related GIS data for nationwide cohort.  Calculation of estimated driving times between accident locations and major trauma centers using Google Maps API.
\end{list1}

\textsl{Traffic Exposures for Rush University Medical Center} \\
Collaborators:  Christopher Codispoti\\
\vspace{-0.13in}
\begin{list1}
\item[] Geocoding and GIS calculation of traffic related variables for a cohort of subject in the Chicago, IL area.
\end{list1}

\section{\sc Conference Presentations}
\begin{list3} \itemsep 4pt
\item[] \textbf{Brokamp C}, Jandarov R, Rao MB, LeMasters G, Ryan PH. Land Use Models for Elemental Components of Particulate Matter in an Urban Environment: A Comparison of Regression and Random Forest Models. A talk given at the International Society of Exposure Science Annual Meeting, October 2016, Utrecht, NL.
\item[] \textbf{Brokamp C}, LeMasters G, Ryan PH. Childhood Residential Changes are Associated with Decreased Traffic Exposure and Improved Neighborhood Characteristics. A talk given at the International Society of Exposure Science Annual Meeting, October 2015, Las Vegas, NV.
%\item[] Tan JS, \textbf{Brokamp C}, LeMasters G, Bernstein DI, Lockey JE, Hershey GK, Villareal M, Ryan P. Longitudinal Patterns of Skin Prick Test Sensitization in Early Childhood Predicts Risk for Asthma at age 7. A poster presented at the American Academy of Allergy, Asthma \& Immunology Annual Meeting, February 2015, Houston, TX.
%\item[] Schmidlin KA, \textbf{Brokamp C}, LeMasters G, Bernstein DI, Lockey JE, Hershey GK, Ryan P. Distinct Phenotypes of Childhood Asthma: Cluster Analysis in a Longitudinal Birth Cohort. A poster presented at the American Academy of Allergy, Asthma \& Immunology Annual Meeting, February 2015, Houston, TX.
\item[] \textbf{Brokamp C}, Appel K, Welge J, Mossman D, Barzman D. Brief Rating of Aggression by Children and Adolescents (BRACHA) 1.0.  A poster presented at the American Academy of Psychiatry and the Law conference, October 2014, Chicago, IL. 
%\item[] Chatterjee K, Ryan P, Grinshpun S, Schaffer C, \textbf{Brokamp C}, Adamkiewicz G, Chew G, Chillrud S, Ross J, Reponen T. Exposure to PM2.5, Ultrafine and Black Carbon Particles in Green vs. Non-Green Homes. A poster presented at the International Society of Exposure Science Conference, October 2014, Cincinnati, OH.
\item[] \textbf{Brokamp C}, Rao MB, Ryan P. Assessing the Improvement in Predicting Personal Exposure to Elements in PM2.5 by Including Indoor PM2.5 Measurements and Home Characteristics to Outdoor PM2.5 Measurements.  A poster presented at the International Society of Exposure Science Conference, October 2014, Cincinnati, OH.
\item[] \textbf{Brokamp C}, Rao MB, Ryan P. Assessing Personal PM2.5 Exposure Prediction Improvement After Addition of Indoor PM2.5 Exposure and Personal Characteristics to Outdoor PM2.5 Exposure Measurements. A poster and speed oral presentation at the Joint Statistical Meeting, August 2014, Boston, MA.
\item[] \textbf{Brokamp C}, Rao MB, Ryan P. Assessing the Improvement in Predicting Personal Exposure to Elements in PM2.5 by Including Indoor PM2.5 Measurements and Home Characteristics to Outdoor PM2.5 Measurements. A poster presented at the Health Effects Institute Conference, May 2014, Alexandria, VA.
\item[] \textbf{Brokamp C}, Wendell D, Montemagno C. Electrophysiology and Plaque Formation of Cx43 Hemichannels.  A poster presented at the Biophysical Society Conference, March 2010, San Francisco, CA.
\item[] \textbf{Brokamp C}, Wendell D, Montemagno C. Exogenous Control of Gene Expression in Insect Cells via Ribozyme Modulation. A poster presented at the Biophysical Society Conference, March 2009, Boston, MA.
\item[] \textbf{Brokamp C}, Wendell D, Montemagno C.  The Engineering and Conductance of a Membrane Bound Nanopore from the Phi29 Portal Protein GP10.  A poster presented at the Biophysical Society Conference, March 2009, Boston, MA.
\item[] \textbf{Brokamp C}, Wendell D, Montemagno C. Exogenous Control of Gene Expression in Insect Cells via Ribozyme Modulation.  A poster presented at the University of Cincinnati Undergraduate Poster Symposium, June 2008, Cincinnati, OH.
\item[] \textbf{Brokamp C}, Wendell D, Montemagno C. Engineering the Calvin Cycle: A Cell Free Photoconversion System for Biofuel Generation.  A poster presented at the University of Cincinnati Undergraduate Poster Symposium, June 2008, Cincinnati, OH.
\end{list3}

\section{\sc Seminar Presentations}
\begin{list3} \itemsep 4pt
\item[] \textbf{Brokamp C}. Combined Sewer Overflow and Childhood Hospital Admissions. A presentation for the Division of Biostatistics and Epidemiology seminar series at Cincinnati Children's Hospital Medical Center, June 2016, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Geospatial Data for Environmental Epidemiology. A seminar presentation for the Environmental Epidemiology Shared Interest Group at Cincinnati Children's Hospital Medical Center, February 2016, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Confidence Intervals for Random Forest Predictions Using the Infinitesimal Jackknife. A seminar presentation for the University of Cincinnati Division of Biostatistics and Bioinformatics, November 2015, Cincinnati, OH.
\item[] \textbf{Brokamp C}. R Studio and R Markdown: An integrated IDE and report generator for R. A guest lecture for BE7022 (Intro To Biostatistics), University of Cincinnati, September 2015, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Does the Elemental Composition of Indoor and Outdoor PM2.5 Accurately Represent the Elemental Composition of Personal PM2.5? A seminar presentation for the University of Cincinnati Division of Biostatistics and Epidemiology, September 2014, Cincinnati, OH. 
\item[] \textbf{Brokamp C}. Exact Sampling and Counting for Fixed-Margin Matrices.  A seminar presentation for University of Cincinnati Biostatistics and Epidemiology, September 2013, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Calculating Correct Standard Errors from Subsets of Complex Sampling Designs in R.  A seminar presentation for University of Cincinnati Biostatistics and Epidemiology, August 2013, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Statistical Analysis of Microarray Data: Controlling the False Discovery Rate.  A seminar presentation for BE 7089, University of Cincinnati Biostatistics and Epidemiology, October 2012, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Small Molecule Disruption of G Beta Gamma Signaling Inhibits the Progression of Heart Failure.  A seminar presentation for the University of Cincinnati Department of Pharmacology and Biophysics, November 2011, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Ultrasound-Targeted Microbubble Destruction to Deliver Nucleic Acid to the Heart.  A seminar presentation for the University of Cincinnati Department of Pharmacology and Biophysics, March 2011, Cincinnati, OH.
\item[] \textbf{Brokamp C}. An academic research cooperative education experience. A seminar presentation for BME 321, University of Cincinnati Biomedical Engineering, February 2011, Cincinnati, OH.
\item[] \textbf{Brokamp C}. Chronopharmacology: The Role of the Circadian Clock in Pharmacology.  A seminar presentation for the University of Cincinnati Department of Pharmacology and Biophysics, January 2011, Cincinnati, OH.
\end{list3}



\section{\sc Computer Skills} 

\begin{list3} \itemsep 4pt
\item[] \textit{Statistical Packages:}  R (including GIS packages: rgdal, rgeos, sp, raster)
\item[] \textit{Languages:} Python, Unix shell scripting, R Markdown, Max
\item[] \textit{Applications:} RShiny, Knitr, \LaTeX, MS Office, qGIS, ArcGIS, GEOS, LSF 
\item[] \textit{Operating Systems:}  Unix/Linux, Mac, Windows\\ 
\end{list3}

\section{\sc Software}

\texttt{RFinfer}
\begin{list1} \itemsep 2pt
\item[] A package for R that implements novel versions of the random forest from my dissertation research, produces confidence intervals and prediction variances.
\item[] Available at \texttt{https://github.com/cole-brokamp/RFinfer}
\item[] DOI: \texttt{10.5281/zenodo.50879}
\end{list1}

\texttt{aiRpollution}
\begin{list1} \itemsep 2pt
\item[] A package for R that assesses exposure to air pollution components in Cincinnati, Ohio.  Also includes other convience functions for extracting Cincinnati GIS variables.
\item[] Available at \texttt{https://github.com/cole-brokamp/aiRpollution}
\item[] DOI: \texttt{10.5281/zenodo.50878}
\end{list1}

\texttt{geocoder}
\begin{list1} \itemsep 2pt
\item[] A software package for linux that geocodes using TIGER/Line data.  Offline geocoding is useful when dealing with private health information. This software is also implemented on a internal server, available to researchers at CCHMC.
\item[] Available at \texttt{https://github.com/cole-brokamp/geocoder}
\item[] DOI: \texttt{10.5281/zenodo.56484}
\end{list1}

\texttt{geocodeCAGIS}
\begin{list1} \itemsep 2pt
\item[] A package for R that uses exact address files from CAGIS to geocode addresses in Cincinnati, Ohio.
\item[] Available at \texttt{https://github.com/cole-brokamp/geocodeCAGIS}
\item[] DOI: \texttt{10.5281/zenodo.50876}
\end{list1}

\texttt{CB}
\begin{list1} \itemsep 2pt
\item[] A package for R that covers my commonly used personal functions. Includes data exploration functions common to epidemiologic studies. 
\item[] Available at \texttt{https://github.com/cole-brokamp/CB}
\item[] DOI: \texttt{10.5281/zenodo.50877}
\end{list1}

\texttt{Location-based Pollution Exposure}
\begin{list1} \itemsep 2pt
\item[] A portable R Shiny web application that generates predictions of traffic related air pollution exposures based on location.  Supports interactive mapping as well as batch submission of addresses.
\item[] Available at \texttt{http://colebrokamp.com}
\end{list1}

\texttt{Other Projects}
\begin{list1} \itemsep 2pt
\item[] My contributions to open source projects and more software currently under development.
\item[] Available at \texttt{https://github.com/cole-brokamp}
\end{list1}

 

\section{\sc Awards and Memberships} 

\begin{list3} \itemsep 4pt   
\item[] CCHMC Arnold W. Strauss Fellow Award \hfill \textit{2016}
\item[] CCHMC Division of Biostatistics \& Epidemiology Travel Award \hfill \textit{2016}
\item[] Member - International Society of Exposure Science \hfill \textit{2014 -- present}
\item[] Member - American Statistical Assocation \hfill \textit{2013 -- present}
\item[] Choose Ohio First Scholarship Recipient \hfill \textit{2010 -- 2015}
\item[] University Graduate Scholarship Recipient \hfill \textit{2010 -- present}
\item[] Distinguished Honors Scholar, UC Engineering \hfill \textit{2010}
\item[] University of Cincinnati Alumni Scholarship \hfill \textit{2008 -- 2009}
\item[] University Cincinnatus Scholar Recipient \hfill \textit{2005 -- 2010}
\end{list3}


\section{\sc Leadership and Service} 
\begin{list3} \itemsep 4pt     
\item[] Co-founded Biostatistics Student Journal Club, \\Department of Biostatistics, University of Cincinnati\hfill \textit{2013} 
\item[] Student Representative to Graduate Education Committee, \\Department of Pharmacology, University of Cincinnati \hfill \textit{2010 -- 2011}
\end{list3}


\end{resume}
\end{document}




