---
title: 'Probability and Odds Ratios'
---

Interpreting a logistic regression model often requires thinking in terms of odds ratios.  This post attempts to illustrate the odds ratio relationship with probability.

Create a vector of probabilities and translate it to odds $\frac{p(x=1)}{p(x=0)}$.

```{r}
probs <- seq(0.15,0.51,by=0.001)
odds <- probs/(1-probs)
```

Plot the odds for each probability.

```{r}
plot(probs,odds,type='l')
```

Next, create the odds ratio for each combination of the odds.

```{r}
odds.ratio <- sapply(odds, function(x) x / odds)
```

Plot the resulting odds ratio for each combination of probabilites.  Use the countour colors and labels to read the odds ratio. For example, if the probability of an event in the unexposed group is 15% and the resulting odds ratio from an exposure is 2, then the probability of an event in the exposed group is about 26%.

```{r cache=TRUE}
image(x=probs,y=probs,z=odds.ratio,col=heat.colors(256))
contour(x=probs,y=probs,z=odds.ratio,add=TRUE,drawlabels=TRUE,
        levels=c(0.5,1,1.25,1.5,1.75,2,3,4,5))
```




