\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\date{}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}

\textbf{Cole Brokamp} and Patrick Ryan. Land use models for eleven
elemental components of particulate matter in an urban environment: A
comparison of linear regression and random forest models. {[}In
preparation.{]}

Jennifer Kannan, \textbf{Cole Brokamp}, David I. Bernstein, James E.
Lockey, Manuel Villareal, Gurjit K. Khurana Hershey, Grace K. LeMasters,
and Patrick Ryan. Clinical and environmental factors associated with
habitual snoring in the cincinnati childhood allergy and air pollution
study. {[}In preparation.{]}

Kristin A. Schmidlin, \textbf{Cole Brokamp}, Grace K. LeMasters, David
I. Bernstein, James E. Lockey, Manuel Villareal, Gurjit K. Khurana
Hershey, and Patrick Ryan. Cluster analysis of childhood asthma
phenotypes identifies specific environmental risk factors. {[}In
preparation.{]}

Jessica S. Tan, \textbf{Cole Brokamp}, David I. Bernstein, Grace K.
LeMasters, Gurjit K. Khurana Hershey, James E. Lockey, Manuel Villareal,
and Patrick Ryan. Patterns of longitudinal allergic sensitization
identifies phenotypes of children at increased risk for asthma. {[}In
preparation.{]}

Patrick Ryan, James E. Lockey, Brad Black, Carol H. Rice, Jeff Burkle,
Tim Hilbert, Linda Levin, \textbf{Cole Brokamp}, Roy McKay, Ted Larson,
and Grace K. LeMasters. Childhood exposure to libby amphibole asbestos
and respiratory symptoms in young adulthood. {[}Submitted.{]}

\textbf{Cole Brokamp}, Grace LeMasters, and Patrick Ryan. Residential
mobility impacts exposure assessment and community socioeconomic
characteristics in longitudinal epidemiology studies. {[}In Press -
Journal of Exposure Science and Environmental Epidemiology.{]}

Kanistha C. Coombs, Ginger L. Chew, Christopher Schaffer, Patrick H.
Ryan, \textbf{Cole Brokamp}, Sergey A. Grinshpun, Gary Adamkiewicz,
Steve Chillrude, Curtis Hedman, Meryl Colton, Jamie Ross, and Tiina
Reponen. Indoor air quality in green vs.~non-green low-income homes of
asthmatic children living in a temperate region of US (Ohio).
{[}Submitted.{]}

\textbf{Cole Brokamp}, MB Rao, Z-H Fan, and Patrick Ryan. Analysis of
personal and home characteristics associated with the elemental
composition of PM2.5 in indoor, outdoor, and personal air in the RIOPA
study. {[}In press - Health Effects Institute.{]}

Kelly J Brunst, Patrick H Ryan, \textbf{Cole Brokamp}, David Bernstein,
Tiina Reponen, James Lockey, Gurjit K Khurana Hershey, Linda Levin,
Sergey A Grinshpun, and Grace LeMasters. Timing and duration of
traffic-related air pollution exposure and the risk for childhood wheeze
and asthma. American journal of respiratory and critical care medicine,
(ja), 2015.
\href{https://github.com/cole-brokamp/cole-brokamp.github.io/raw/master/publications/rccm\%252E201407-1314oc.pdf}{{[}download{]}}

Patrick H Ryan, Sang Young Son, Christopher Wolfe, James Lockey,
\textbf{Cole Brokamp}, and Grace LeMasters. A field application of a
personal sensor for ultrafine particle exposure in children. Science of
The Total Environment, 508:366-373, 2015.
\href{https://github.com/cole-brokamp/cole-brokamp.github.io/raw/master/publications/1-s2.0-S0048969714016556-main.pdf}{{[}download{]}}

\textbf{Cole Brokamp}, MB Rao, Zhihua Tina Fan, and Patrick H Ryan. Does
the elemental composition of indoor and outdoor PM2.5 accurately
represent the elemental composition of personal PM2.5? Atmospheric
Environment, 101:226-234, 2015.
\href{https://github.com/cole-brokamp/cole-brokamp.github.io/raw/master/publications/1-s2.0-S1352231014008814-main.pdf}{{[}download{]}}

\textbf{Cole Brokamp}, Jacob Todd, Carlo Montemagno, and David Wendell.
Electrophysiology of single and aggregate cx43 hemichannels. PLoS ONE,
7(10):e47775, 2012.
\href{https://github.com/cole-brokamp/cole-brokamp.github.io/raw/master/publications/journal.pone.0047775.pdf}{{[}download{]}}

Sheryl E Koch, Xiaoqian Gao, Lauren Haar, Min Jiang, Valerie M Lasko,
Nathan Robbins, Wenfeng Cai, \textbf{Cole Brokamp}, Priyanka Varma,
Michael Tranter, et al. Probenecid: novel use as a non-injurious
positive inotrope acting via cardiac trpv2 stimulation. Journal of
molecular and cellular cardiology, 53(1):134-144, 2012.
\href{https://github.com/cole-brokamp/cole-brokamp.github.io/raw/master/publications/nihms-373871.pdf}{{[}download{]}}

Michael Tranter, Robert N Helsley, Waltke R Paulding, Michael
McGuinness, \textbf{Cole Brokamp}, Lauren Haar, Yong Liu, Xiaoping Ren,
and W Keith Jones. Coordinated post-transcriptional regulation of hsp70.
3 gene expression by microrna and alternative polyadenylation. Journal
of Biological Chemistry, 286(34):29828-29837, 2011.
\href{https://github.com/cole-brokamp/cole-brokamp.github.io/raw/master/publications/J.\%20Biol.\%20Chem.-2011-Tranter-29828-37.pdf}{{[}download{]}}

\end{document}
