\textbf{Efficient and Secure High Resolution Spatiotemporal Exposure
Assessment}. \emph{International Society of Exposure Science Annual
Meeting}. Online. 2021.

\textbf{Decentralized, Efficient, and Secure High Resolution
Spatiotemporal Exposure Assessment at Scale}. \emph{NIH Integrating
Multiscale Geospatial Environmental Data into Large Population Health
Studies Workshop}. Online. 2021.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/brokamp_DeGAUSS_16_06_2020.pdf}{\emph{Download}}.

\textbf{Decentralized and Reproducible Geocoding and Geomarker
Assessment for Multi-Site Studies}. \emph{Pediatric Acute Care
Cardiology Collaborative Spring Conference}. Online. 2021.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/DeGAUSS_quick_pitch_PAC3.pdf}{\emph{Download}}.

\textbf{Geomarkers and Health}. \emph{Rutgers University Social
Epidemiology guest lecture}. Online. 2021.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/deprivation_index.pdf}{\emph{Download}}.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures at Scale}. \emph{University of
Cincinnati Biomedical Informatics Practicum (BMIN8001) guest lecture}.
Cincinnati, OH. 2021.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/brokamp_degauss_2021_02_01.pdf}{\emph{Download}}.

\textbf{Three Levels of Computational Mobility in R}. \emph{SatRday
Columbus}. Virtual. 2020.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/cole_brokamp_three_levels_of_computational_mobility.pdf}{\emph{Download}}.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures at Scale}. \emph{Pediatric
Musculoskeletal \& Rheumatology Innovation Core Center Seminar Series}.
Virtual. 2020.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/brokamp_degauss_2020_10_27.pdf}{\emph{Download}}.

\textbf{Introduction to Geoinformatics for Precision Population Health}.
\emph{University of Cincinnati Introduction to Medical Informatics
course guest lecture}. Cincinnati, OH. 2020.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/GRAPPH_talk_informatics_2020.pdf}{\emph{Download}}.

\textbf{Short-term Ambient Fine Particulate Matter and Anxiety Symptoms
in Adolescents with Generalized Anxiety Disorder}. \emph{International
Society of Environmental Epidemiology Annual Meeting}. Virtual. 2020.

\textbf{Decentralized Geomarker Assessment for Multi-Site Studies
(DeGAUSS)}. \emph{UseR! 2020 Conference (Conference Canceled)}.
St.~Louis, MO. 2020.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures at Scale}. \emph{University of
Cincinnati Biomedical Informatics Practicum (BMIN8001) guest lecture}.
Cincinnati, OH. 2020.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/brokamp_degauss_2020_02_24.pdf}{\emph{Download}}.

\textbf{Pediatric Psychiatric Emergency Department Utilization and Fine
Particulate Matter: A Case-Crossover Study}. \emph{University of
Cincinnati Department of Epidemiology Seminar}. Cincinnati, OH. 2020.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/talks/brokamp_PM_psych_ED_2020_01_23.pdf}{\emph{Download}}.

\textbf{Using Twitter for Academic Networking}. \emph{Cincinnati
Children's Faculty Career Development Seminar Series}. Cincinnati, OH.
2019.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/twitter_for_academia.html}{\emph{Download}}.

\textbf{Causal Inference Machine Learning Methods for Identifying
Subpopulations Susceptible to the Health Effects of Air Pollution}.
\emph{Cincinnati Children's Machine Learning Focus Group}. Cincinnati,
OH. 2019.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/brokamp_hce_2019_11_06.pdf}{\emph{Download}}.

\textbf{Non-Parametric and Data-Driven Methods for Identifying
Subpopulations Susceptible to the Health Effects of Air Pollution}.
\emph{International Biometric Society (Eastern North American Region)
Spring Meeting}. Philadelphia, PA. 2019.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/brokamp_hce_ENAR2019.pdf}{\emph{Download}}.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures at Scale}. \emph{Center for
Clinical \& Translational Science \& Training Grand Rounds}. Cincinnati,
OH. 2019.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/brokamp_degauss_2019_15MAR2019.pdf}{\emph{Download}}.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures at Scale}. \emph{Northwestern
Institute for Public Health and Medicine Seminar Series}. Chicago, IL.
2018.

\textbf{Introduction to Geoinformatics for Precision Population Health}.
\emph{University of Cincinnati Introduction to Medical Informatics
course guest lecture}. Cincinnati, OH. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/GRAPPH_talk_informatics_2018.pdf}{\emph{Download}}.

\textbf{Reproducible Research in R: Geoinformatics, Epidemiology, and
Publicly Available Health and GIS Data}. \emph{Workshop at the American
College of Epidemiology Annual Meeting}. Cincinnati, OH. 2018.
\href{https://github.com/cole-brokamp/geoinformatics_and_population_health_in_R}{\emph{Download}}.

\textbf{Climate Change and Health Disparities in the Urban Environment}.
\emph{University of Cincinnati Research and Innovation Week}.
Cincinnati, OH. 2018.

\textbf{Geoinformatics for Environmental Epidemiology}. \emph{Biomedical
Informatics (BMIN8001) Practicum Guest Lecture}. Cincinnati, OH. 2018.

\textbf{Hot Topics in Pediatric Research Methodology: CART and Random
Forest}. \emph{Pediatric Academic Society Annual Meeting}. Toronto, ON.
2018.

\textbf{Ensemble Machine Learning for Air Pollution Exposure
Assessment}. \emph{American Statistical Association, Cincinnati Chapter
Meeting}. Cincinnati, OH. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/LURF_talk_20_FEB_2018.pdf}{\emph{Download}}.

\textbf{Combined Sewer Overflow Events and Childhood Emergency
Department Visits: A Case-Crossover Study}. \emph{University of
Cincinnati Environmental Health Seminar}. Cincinnati, OH. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/cso_talk_30_November_2017.pdf}{\emph{Download}}.

\textbf{The Cincinnati Childhood Allergy and Air Pollution Study: An
Overview and New Approaches to Exposure Assessment}. \emph{Harvard
School of Public Health Air, Climate \& Energy Center Research Meeting}.
Boston, MA. 2017.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures for Multi-Site Studies}.
\emph{Harvard School of Public Health Air, Climate \& Energy Center
Research Meeting}. Boston, MA. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/DeGAUSS_talk_13_NOV_2017.pdf}{\emph{Download}}.

\textbf{Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures for Multi-Site Studies}.
\emph{International Society of Exposure Science Annual Meeting}.
Research Triangle Park, NC. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/DeGAUSS_talk_ISES2017.pdf}{\emph{Download}}.

\textbf{Assessing Daily Exposure to PM2.5 with Machine Learning and
Remote Sensing}. \emph{International Society of Exposure Science Annual
Meeting}. Research Triangle Park, NC. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/talks/spatiotemporal_pm_model_talk_ISES2017.pdf}{\emph{Download}}.

\textbf{Assessing Daily Exposure to PM2.5 with Machine Learning and
Remote Sensing}. \emph{Cincinnati Children's Hospital Medical Center
Division of Biostatistics and Epidemiology Seminar}. Cincinnati, OH.
2017.

\textbf{Using GRAPPH to Leverage Geoinformatics for Innovative Research,
Place-based Clinical Care, and Community-Centered Quality Improvement}.
\emph{Cincinnati Children's Hospital Medical Center Mayerson Center for
Safe and Healthy Children Quarterly Research Meeting}. Cincinnati, OH.
2017.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/GRAPPH_talk_MayersonCenter_16June2017.pdf}{\emph{Download}}.

\textbf{Combined Sewer Overflow Events and Childhood Emergency
Department Visits: A Case-Crossover Study}. \emph{Cincinnati Children's
Hospital Medical Center Postdoc and Research Associate Meeting}.
Cincinnati, OH. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/cso_talk_3_April_2017.pdf}{\emph{Download}}.

\textbf{Geocoding to Characterize Community and Environmental Exposures
for Multi-site Studies}. \emph{Cincinnati Children's Hospital Medical
Center Division of Biomedical Informatics Hutton Lecture Series}.
Cincinnati, OH. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/DeGAUSS_talk_Hutton.pdf}{\emph{Download}}.

\textbf{GIS Tools for Environmental Epidemiology}. \emph{University of
Cincinnati Biomedical Informatics (BMIN8001) Practicum course guest
lecture}. Cincinnati, OH. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/BMIN8001_environmental_epidemiology.pdf}{\emph{Download}}.

\textbf{Building A Platform for Data Sharing}. \emph{Cincinnati
Children's Hospital Medical Center Academy Health Site Visit}.
Cincinnati, OH. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/academy_health_visit.pdf}{\emph{Download}}.

\textbf{Land Use Models for Elemental Components of Particulate Matter
in an Urban Environment: A Comparison of Regression and Random Forest
Models}. \emph{International Society of Exposure Science Annual
Meeting}. Utrecht, NL. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/LUR_vs_LURF_Cole_Brokamp.pdf}{\emph{Download}}.

\textbf{Predictive Comparisons: Interpreting Input Effects for Any
Supervised Learner}. \emph{Cincinnati Children's Hospital Medical Center
Division of Biostatistics \& Epidemiology Journal Club}. Cincinnati, OH.
2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/APC_talk.pdf}{\emph{Download}}.

\textbf{Land Use Models for Elemental Components of Particulate Matter
in an Urban Environment: A Comparison of Regression and Random Forest
Models}. \emph{University of Cincinnati Division of Biostatistics and
Bioinformatics Seminar Series}. Cincinnati, OH. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/LUR_vs_LURF_Cole_Brokamp.pdf}{\emph{Download}}.

\textbf{Data Visualization for Population Health Initiatives}. \emph{All
In Data Visualization Webinar}. Cincinnati, OH. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/all_in_webinar_Beck_Brokamp.pdf}{\emph{Download}}.

\textbf{Using Machine Learning and Interactive Dashboards to Understand
How Children's Health is Impacted by their Community and Surrounding
Environment}. \emph{University of Cincinnati Institute for Analytics
Innovation Showcase and Networking Event}. Cincinnati, OH. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/data_analytics_showcase_cole_brokamp.pdf}{\emph{Download}}.

\textbf{Combined Sewer Overflow and Childhood Hospital Admissions}.
\emph{Cincinnati Children's Hospital Medical Center Division of
Biostatistics \& Epidemiology Seminar Series}. Cincinnati, OH. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/Combined\%20Sewer\%20Overflow\%20and\%20Hospital\%20Admissions.pdf}{\emph{Download}}.

\textbf{Land Use Random Forests for Estimation of Exposure to Elemental
Components of Particulate Matter}. \emph{University of Cincinnati
Division of Biostatistics and Bioinformatics Doctoral Dissertation
Defense}. Cincinnati, OH. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/Cole\%20Brokamp\%20Dissertation\%20Defense\%2023March2016.pdf}{\emph{Download}}.

\textbf{Geospatial Data for Environmental Epidemiology}.
\emph{Cincinnati Children's Hospital Medical Center Environmental
Epidemiology Shared Interest Group Seminar Series}. Cincinnati, OH.
2016.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/GIS_env_epi.pdf}{\emph{Download}}.

\textbf{Confidence Intervals for Random Forest Predictions Using the
Infinitesimal Jackknife}. \emph{University of Cincinnati Division of
Biostatistics and Bioinformatics Seminar Series}. Cincinnati, OH. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/Confidence_Intervals_for_Random_Forest_Predictions_Using_the_Infinitesimal_Jackknife.pdf}{\emph{Download}}.

\textbf{Childhood Residential Changes are Associated with Decreased
Traffic Exposure and Improved Neighborhood Characteristics}.
\emph{International Society of Exposure Science Annual Meeting}. Las
Vegas, NV. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/Cole_Brokamp_ISES_2015.pdf}{\emph{Download}}.

\textbf{R Studio and R Markdown: An integrated IDE and report generator
for R}. \emph{University of Cincinnati BE7022 (Intro To Biostatistics)
Guest Lecture}. Cincinnati, OH. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/talks/RStudio_and_RMarkdown.pdf}{\emph{Download}}.

\textbf{Does the Elemental Composition of Indoor and Outdoor PM2.5
Accurately Represent the Elemental Composition of Personal PM2.5?}.
\emph{University of Cincinnati Division of Epidemiology Seminar Series}.
Cincinnati, OH. 2014.

\textbf{Assessing Personal PM2.5 Exposure Prediction Improvement After
Addition of Indoor PM2.5 Exposure and Personal Characteristics to
Outdoor PM2.5 Exposure Measurements}. \emph{Joint Statistical Meeting}.
Boston, MA. 2014.

\textbf{Exact Sampling and Counting for Fixed-Margin Matrices}.
\emph{University of Cincinnati Division of Epidemiology Seminar Series}.
Cincinnati, OH. 2013.

\textbf{Small Molecule Disruption of G Beta Gamma Signaling Inhibits the
Progression of Heart Failure}. \emph{University of Cincinnati Department
of Pharmacology and Biophysics Seminar Series}. Cincinnati, OH. 2011.

\textbf{Ultrasound-Targeted Microbubble Destruction to Deliver Nucleic
Acid to the Heart}. \emph{University of Cincinnati Department of
Pharmacology and Biophysics Seminar Series}. Cincinnati, OH. 2011.

\textbf{An academic research cooperative education experience}.
\emph{University of Cincinnati BME321 Guest Lecture}. Cincinnati, OH.
2011.
