Todd Florin, Lilliam Ambroggio, \textbf{Cole Brokamp}, Yin Zhang,
Mantosh Rattan, Eric Crotty, Michael A Belsky, Sara Krueger, Thomas N
Epperson, Andrea Kachelmeyer, Richard Ruddy, Samir S Shaw. Biomarkers
and Disease Severity in Children with Community-Acquired Pneumonia.
\emph{Pediatrics}. online. 2020.

Rhonda Szczesniak, Jessica L. Rice, \textbf{Cole Brokamp}, Patrick Ryan,
Teresa Pestian, Yizhao Ni, Eleni-Rosalina Andrinopoulou, Ruth H. Keogh,
Emrah Gecili, Rui Huang, John P. Clancy, Joseph M. Collaco. Influences
of Environmental Exposures On Individuals Living with Cystic Fibrosis.
\emph{Expert Review of Respiratory Medicine}. online. 2020.

Zana Percy, \textbf{Cole Brokamp}, Jennifer M McAllister, Patrick Ryan,
Scott L Wexelblatt, Eric Hall. Subclinical and Overt Newborn Opioid
Exposure: Prevalence and First Year Healthcare Utilization.
\emph{Journal of Pediatrics}. online. 2020.

Sharad Wadhwani, John Bucuvalas, \textbf{Cole Brokamp}, Ravinder Anand,
Ashutosh Gupta, Stuart Taylor, Eyal Shemesh, Andrew Beck. Association
Between Neighborhood-level Socioeconomic Deprivation and the Medication
Level Variability Index for Children Following Liver Transplantation.
\emph{Transplantation}. online. 2020.

Kim Hartley, Patrick Ryan, \textbf{Cole Brokamp}, Gordon L. Gillespie.
Effect of greenness on asthma in children: A systematic review.
\emph{Public Health Nursing}. 37(3). 453-460. 2020.
\href{https://colebrokamp-website.s3.us-east-1.amazonaws.com/publications/Hartley_PHN_2020.pdf}{\emph{Download}}.

Robert M. Rossi, Chris Wolfe, \textbf{Cole Brokamp}, Jennifer M.
McAllister, Scott Wexelblatt, Carri R. Warshak, Eric S. Hall. Reported
Prevalence of Maternal Hepatitis C Virus Infection in the United States.
\emph{Obstetrics \& Gynecology}. 135. 1-10. 2020.

Rhonda D. Szczesniak, Weiji Su, \textbf{Cole Brokamp}, Ruth H. Keogh,
John P. Pestian, Michael Seid, Peter J. Diggle, John P. Clancy. Dynamic
Predictive Probabilities to Monitor Rapid Cystic Fibrosis Disease
Progression. \emph{Statistics in Medicine}. 39. 740-756. 2020.

Sarah Orkin, \textbf{Cole Brokamp}, Toshifumi Yodoshi, Andrew T. Trout,
Chunyan Liu, Syeda Meryum, Stuart Taylor, Christopher Wolfe, Rachel
Sheridan, Aradhna Seth, Mohammad Alfrad Nobel Bhuiyan, Sanita Ley, Ana
Catalina Arce-Clachar, Kristin Bramlage, Robert Kahn, Stavra Xanthakos,
Andrew F. Beck, Marialena Mouzaki. Community Socioeconomic Deprivation
and Non-Alcoholic Fatty Liver Disease Severity. \emph{Journal of
Pediatric Gastroenterology and Nutrition}. 2019.

\textbf{Cole Brokamp}, Jeffrey R. Strawn, Andrew F. Beck, Pat Ryan.
Pediatric Psychiatric Emergency Department Utilization and Fine
Particulate Matter: A Case-Crossover Study. \emph{Environmental Health
Perspectives}. 127(9). 2019.
\href{https://s3.amazonaws.com/colebrokamp-website/publications/Brokamp_EHP_2019.pdf}{\emph{Download}}.

Erica Andrist, \textbf{Cole Brokamp}, Stuart Taylor, Carley Riley,
Andrew Beck. Neighborhood Poverty and Pediatric Intensive Care Use.
\emph{Pediatrics}. 2019.

\textbf{Cole Brokamp}, Eric B. Brandt, Patrick H. Ryan. Assessing
Exposure to Outdoor Air Pollution for Epidemiological Studies:
Model-based and Personal Sampling Strategies. \emph{Journal of Allergy
and Clinical Immunology}. 2019.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JACI_2019.pdf}{\emph{Download}}.

Lilliam Ambroggio, \textbf{Cole Brokamp}, Rachel Mantyla, Brad DePaoli,
Richard Ruddy, Samir Shah, Todd Florin. Validation of the British
Thoracic Society Severity Criteria for Pediatric Community-Acquired
Pneumonia. \emph{Pediatric Infectious Diseases Journal}. 2019.

Rebecca Gernes, \textbf{Cole Brokamp}, Glenn Rice, J. Michael Wright,
Michelle Kondo, Yvonne Michael, Geoffrey Donovan, Demetrios Gatziolis,
David Bernstein, Grace LeMasters, James Lockey, G. Khurana Hershey,
Patrick Ryan. Using high-resolution residential greenspace measures in
an urban environment to assess risks of allergy outcomes in a cohort of
children. \emph{Science of the Total Environment}. 668. 760-767. 2019.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Gernes-Using\%20high-resolution\%20residential\%20greenspace\%20measures\%20in\%20an\%20urban\%20environment\%20to\%20assess\%20risks\%20of\%20allergy\%20outcomes\%20in\%20children-STE2019.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Andrew F. Beck, Neera K. Goyal, Patrick Ryan,
James M. Greenberg, Eric S. Hall. Material Community Deprivation and
Hospital Utilization During the First Year of Life: An Urban
Population-Based Cohort Study. \emph{Annals of Epidemiology}. 30. 37-43.
2019.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_AoE_2019.pdf}{\emph{Download}}.

Juliana Madzia, Patrick Ryan, Kimberly Yolton, Zana Percy, Nick Newman,
Grace LeMasters, \textbf{Cole Brokamp}. Residential Greenspace Is
Associated with Childhood Behavioral Outcomes. \emph{Journal of
Pediatrics}. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Madzia_JPeds_2018.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}. DeGAUSS: Decentralized Geomarker Assessment for
Multi-Site Studies. \emph{Journal of Open Source Software}. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JOSS_2018.pdf}{\emph{Download}}.

Rhonda D. Szczesniak, \textbf{Cole Brokamp}, Weiji Su, Gary L. McPhail,
John Pestian, and John P. Clancy. Improving Detection of Rapid Cystic
Fibrosis Disease Progression---Early Translation of a Predictive
Algorithm into a Point-of-Care Tool. \emph{IEEE Journal of Translational
Engineering in Health and Medicine}. 7(1). 1-8. 2019.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Szczesniak_IEEE_2018.pdf}{\emph{Download}}.

Lauren C. Riney, \textbf{Cole Brokamp}, Andrew F. Beck, Wendy Pomerantz,
Hamilton Schwartz, Todd A. Florin. Emergency Medical Services
Utilization is Associated with Community Deprivation in Children.
\emph{Prehospital Emergency Care}. Online ahead of print. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Riney_PrehospitalEmergencyCare_2018.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Roman Jandarov, Monir Hossain, Patrick Ryan.
Predicting Daily Urban Fine Particulate Matter Concentrations Using
Random Forest. \emph{Environmental Science \& Technology}. 52 (7).
4173-4179. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_EST_2018_onlineaheadofprint.pdf}{\emph{Download}}.

Andrew F. Beck, Carley L. Riley, Stuart Taylor, \textbf{Cole Brokamp},
Robert S. Kahn. Toward a Culture of Health in Hospitals: Pervasive
population disparities in inpatient bed-day rates across conditions and
subspecialties. \emph{Health Affairs}. 37(4). 551-559. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Beck_HealthAffairs_2018.pdf}{\emph{Download}}.

Todd A. Florin, \textbf{Cole Brokamp}, Rachel Mantyla, Bradley DePaoli,
Richard Ruddy, Samir S. Shah, Lilliam Ambroggio. Validation of the
IDSA/PIDS Severity Criteria in Children with Community-Acquired
Pneumonia. \emph{Clinical Infectious Diseases}. ciy031. 1-29. 2018.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Florin_ClinicalInfectiousDiseases_2018.pdf}{\emph{Download}}.

Rhonda Szczesniak, \textbf{Cole Brokamp}, Weiji Su, Gary L. McPhail,
John Pestian, John P. Clancy. Early Detection of Rapid Cystic Fibrosis
Disease Progression Tailored to Point of Care: A Proof-of-Principle
Study. \emph{Healthcare Innovations and Point of Care Technologies}.
(HI-POCT), 2017 IEEE. 204-207. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Szczesniak_IEEE_2017.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, MB Rao, Patrick Ryan, Roman Jandarov. A
comparison of resampling and recursive partitioning methods in random
forest for estimating the asymptotic variance using the infinitesimal
jackknife. \emph{Stat}. 6(1). 360-372. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_Stat_2017.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Chris Wolfe, Todd Lingren, John Harley, Patrick
Ryan. Decentralized and Reproducible Geocoding and Characterization of
Community and Environmental Exposures for Multi-Site Studies.
\emph{Journal of American Medical Informatics Association}. 25(3).
309-314. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JAMIA_2017.pdf}{\emph{Download}}.

Rhonda D. Szczesniak, Dan Li, Weiji Su, \textbf{Cole Brokamp}, John
Pestian, Michael Seid, John P. Clancy. Phenotypes of Rapid Cystic
Fibrosis Lung Disease Progression during Adolescence and Young
Adulthood. \emph{American Journal of Respiratory And Critical Care
Medicine}. 196(4). 471-478. 2017.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Szczesniak_AJRCCM_2017.pdf}{\emph{Download}}.

Todd Florin, Lilliam Ambroggio, \textbf{Cole Brokamp}, Mantosh S.
Rattan, Eric J. Crotty, Andrea Kachelmeyer, Richard M. Ruddy, Samir
Shah. Reliability of Examination Findings in Suspected
Community-Acquired Pneumonia. \emph{Pediatrics}. 140(3). e20170310.
2017.
\href{https://colebrokamp-website.s3.amazonaws.com/publications/Florin_Pediatrics_2017.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Andrew F. Beck, Louis Muglia, Patrick Ryan.
Combined Sewer Overflow Events and Childhood Emergency Department
Visits: A Case-Crossover Study. \emph{Science of the Total Environment}.
607-608. 1180-1187. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_STOTEN_2017.pdf}{\emph{Download}}.

Patrick Ryan, James E. Lockey, Brad Black, Carol H. Rice, Jeff Burkle,
Tim Hilbert, Linda Levin, \textbf{Cole Brokamp}, Roy McKay, Ted Larson,
Grace K. LeMasters. Childhood exposure to libby amphibole asbestos and
respiratory symptoms in young adulthood. \emph{Environmental Research}.
158. 470-479. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Ryan_EnvRes_2017.pdf}{\emph{Download}}.

Lusine Yaghjyan, R Aroa, \textbf{Cole Brokamp}, E O'Meara, B Sprague, G
Ghita, Patrick Ryan. Association of air pollution with mammographic
breast density in the Breast Cancer Surveillance Consortium.
\emph{Breast Cancer Research}. 19:36. 1-10. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Yaghjyan_2017_BreastCancerResearch.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Roman Jandarov, MB Rao, Grace LeMasters, Patrick
Ryan. Exposure assessment models for elemental components of particulate
matter in an urban environment: A comparison of regression and random
forest approaches. \emph{Atmospheric Environment}. 151. 1-11. 2017.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_AtmosEnv_2017.pdf}{\emph{Download}}.

Hong Ji, Jocelyn M Biagini Myers, Eric B Brandt, \textbf{Cole Brokamp},
Patrick H Ryan, Gurjit K Khurana Hershey. Air pollution, epigenetics,
and asthma. \emph{Allergy, Asthma \& Clinical Immunology}. 12(1). 51.
2016.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Ji_AllergyAsthmaClinImmunol_2016.pdf}{\emph{Download}}.

Jennifer Kannan, \textbf{Cole Brokamp}, David I. Bernstein, Grace K.
LeMasters, Gurjit K. Khurana Hershey, Manuel Villareal, James E. Lockey,
Patrick Ryan. Parental Snoring and Environmental Pollutants, but Not
Aeroallergen Sensitization, Are Associated with Childhood Snoring in a
Birth Cohort. \emph{Pediatric Allergy, Immunology, and Pulmonology}. 0.
2016.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Kannan_PedAllImmPul_2016.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Grace LeMasters, Patrick Ryan. Residential
mobility impacts exposure assessment and community socioeconomic
characteristics in longitudinal epidemiology studies. \emph{Journal of
Exposure Science and Environmental Epidemiology}. 26(4). 428-34. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_JESEE_2016.pdf}{\emph{Download}}.

Kanistha C. Coombs, Ginger L. Chew, Christopher Schaffer, Patrick H.
Ryan, \textbf{Cole Brokamp}, Sergey A. Grinshpun, Gary Adamkiewicz,
Steve Chillrude, Curtis Hedman, Meryl Colton, Jamie Ross, Tiina Reponen.
Indoor air quality in green-renovated vs.~non-green low-income homes of
children living in a temperate region of US (Ohio). \emph{Science of The
Total Environment}. 554-555. 178-185. 2016.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Coombs_SciTotEnv_2016.pdf}{\emph{Download}}.

Patrick Ryan, \textbf{Cole Brokamp}, Z-H Fan, MB Rao. Analysis of
personal and home characteristics associated with the elemental
composition of PM2.5 in indoor, outdoor, and personal air in the RIOPA
study. \emph{Health Effects Institute Research Report 185}. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Ryan_HEIReport_2015.pdf}{\emph{Download}}.

Kelly J Brunst, Patrick H Ryan, \textbf{Cole Brokamp}, David Bernstein,
Tiina Reponen, James Lockey, Gurjit K Khurana Hershey, Linda Levin,
Sergey A Grinshpun, Grace LeMasters. Timing and duration of
traffic-related air pollution exposure and the risk for childhood wheeze
and asthma. \emph{American Journal of Respiratory and Critical Care
Medicine}. 192(4). 421-427. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brunst_AmJRespCritCareMed_2015.pdf}{\emph{Download}}.

Patrick H Ryan, Sang Young Son, Christopher Wolfe, James Lockey,
\textbf{Cole Brokamp}, Grace LeMasters. A field application of a
personal sensor for ultrafine particle exposure in children.
\emph{Science of The Total Environment}. 508. 366-373. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Ryan_SciTotEnv_2015.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, MB Rao, Tina Zhihua Fan, Patrick H Ryan. Does the
elemental composition of indoor and outdoor PM2.5 accurately represent
the elemental composition of personal PM2.5?. \emph{Atmospheric
Environment}. 101. 226-234. 2015.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_AtmosEnv_2015.pdf}{\emph{Download}}.

\textbf{Cole Brokamp}, Jacob Todd, Carlo Montemagno David Wendell.
Electrophysiology of single and aggregate Cx43 hemichannels. \emph{PLoS
ONE}. 7(10):e47775. 2012.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Brokamp_PLoSOne_2012.pdf}{\emph{Download}}.

Sheryl E Koch, Xiaoqian Gao, Lauren Haar, Min Jiang, Valerie M Lasko,
Nathan Robbins, Wenfeng Cai, \textbf{Cole Brokamp}, Priyanka Varma,
Michael Tranter, Yong Liu, Xiaoping Ren, John N. Lorenz, Hong-Sheng
Wang, W Keith Jones, Jack Rubinstein. Probenecid: novel use as a
non-injurious positive inotrope acting via cardiac TRPV2 stimulation.
\emph{Journal of Molecular and Cellular Cardiology}. 53(1). 134-144.
2012.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Koch_JMolCellCardiol_2011.pdf}{\emph{Download}}.

Michael Tranter, Robert N Helsley, Waltke R Paulding, Michael
McGuinness, \textbf{Cole Brokamp}, Lauren Haar, Yong Liu, Xiaoping Ren,
W Keith Jones. Coordinated post-transcriptional regulation of HSP70. 3
gene expression by microRNA and alternative polyadenylation.
\emph{Journal of Biological Chemistry}. 286(34). 29828-29837. 2011.
\href{http://colebrokamp-website.s3.amazonaws.com/publications/Tranter_JBiolChem_2011.pdf}{\emph{Download}}.
