---
output:
  word_document:
    reference_docx: reference_biosketch.docx
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


# A. Personal Statement

```{r}
#| child: bio.Rmd
```

In addition, I have contributed as the lead biostatistician in other biomedical clinical and observational studies. I look forward to contributing as a consultant and biostatistician to your proposed R01 project as a part of our ongoing collaborations, which includes NIH-funded awards and co-mentorship of your postdoctoral fellow. My experience and expertise in data processing, statistical methods, as well as analyses and interpretation will contribute to the success of this proposed project.

## Ongoing projects that I would like to highlight include:

```{r}
make_support_entry <- function(x) {
  glue::glue_data(
    x,
    "{source} {number}",
	"{pi_name} (PI)",
    "{start_date} - {end_date}",
    "*{title}*",
    .sep = "  \n", .na = ""
  ) 
}
```

```{r}
#| results: asis
yaml::yaml.load_file("support.yaml") |>
  purrr::keep(\(x) x$status == "Active") |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

## Peer-reviewed publications I would like to highlight include:

```{r}
cite_four <- function(.x) {
  stopifnot(length(.x) <= 4)
  pubs <- yaml::yaml.load_file("pubs.yaml")
  stopifnot(all(.x %in% names(pubs)))
  the_pubs <- purrr::map(.x, \(.) purrr::pluck(pubs, .))
  the_pubs |>
    purrr::map_chr(\(.) glue::glue_data(.,
                           "1",
                           "{paste(author, collapse = ', ')}",
                           "{title}",
                           "*{journal}*",
                           "{issue_pages}",
                           "{year}.",
                           .sep = ". ",
                           .na = character())) |>
    purrr::map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
    cat(sep = "\n\n")
}
```

```{r}
#| results: asis
cite_four(c("vancil-2022", "zundel-2024", "rasnick-2021", "brokamp-2019b"))
```

# B. Positions, Scientific Appointments, and Honors

## Positions

|||
|:-----|:--------------------------|
|2022 – Present |	Associate Professor, Division of Biostatistics and Epidemiology, Cincinnati Children’s Hospital Medical Center, Department of Pediatrics, University of Cincinnati, College of Medicine |
|2017 – 2022 | Assistant Professor, Division of Biostatistics and Epidemiology, Cincinnati Children’s Hospital Medical Center, Department of Pediatrics, University of Cincinnati, College of Medicine|

## Scientific Appointments

|||
|:-----|:------------------|
| 2023 | NIH ZES1 BWD-D (HS) |
| 2023 | NIH ZES1 LWJ-W (K) |
| 2023 | NIH ZES1 LKB-K (P2) |
| 2023 | NIH ZRG1 MCST – B (14) |
| 2023 | NIH ZCTA1 TCRB-J (M2) |
| 2022 | NIH ZES1 WL-W (K) |
| 2022 | NIH ZES1 LWF-S (K9) |
| 2022 | NIH ZES1 LKB-S (KS) |
| 2019 | NIH SIEE study section, early career reviewer |

## Awards

|      |                                                         |
|:-----|:--------------------------------------------------------|
| 2020 | Cincinnati Children's Epidemiology and Biostatistics Top Publication |
| 2017 | Cincinnati Children's Epidemiology and Biostatistics Top Publication and Top Research Achievement |
| 2016 | Cincinnati Children's Arnold Strauss Fellowship Awardee |

# C. Contributions to Science

```{r}
#| child: contrib_science.Rmd
```
