---
output:
  word_document:
    reference_docx: reference_biosketch.docx
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


# A. Personal Statement

```{r}
#| child: bio.Rmd
```

As Carson's primary mentor for this training award, I am committed to providing a rigorous and supportive training environment that will equip him with the skills needed for an independent research career. His proposed training plan is strategically designed to integrate advanced computational methods, interdisciplinary collaboration, and translational research, ensuring he develops expertise in biomedical informatics and environmental epidemiology. Through structured mentorship, hands-on experience, and engagement with clinical and policy stakeholders, Carson will gain the technical proficiency, leadership skills, and professional network necessary to secure external funding and establish his own research program. I am confident that this training plan, combined with Carson’s strong analytical abilities and scientific curiosity, will position him for success as a leader in data-driven public health research.

## Ongoing projects that I would like to highlight include:

```{r}
make_support_entry <- function(x) {
  glue::glue_data(
    x,
    "{source} {number}",
	"{pi_name} (PI)",
    "{start_date} - {end_date}",
    "*{title}*",
    .sep = "  \n", .na = ""
  ) 
}
```

```{r}
#| results: asis
yaml::yaml.load_file("support.yaml") |>
  purrr::keep(\(x) x$status == "Active") |>
  purrr::map_chr(make_support_entry) |>
  cat(sep = "\n\n")
```

## Peer-reviewed publications I would like to highlight include:

These publications were selected to demonstrate my scientific productivity when I am the primary mentor of a clinician-scientist in training:

```{r}
cite_four <- function(.x) {
  stopifnot(length(.x) <= 4)
  pubs <- yaml::yaml.load_file("pubs.yaml")
  stopifnot(all(.x %in% names(pubs)))
  the_pubs <- purrr::map(.x, \(.) purrr::pluck(pubs, .))
  the_pubs |>
    purrr::map_chr(\(.) glue::glue_data(.,
                           "1",
                           "{paste(author, collapse = ', ')}",
                           "{title}",
                           "*{journal}*",
                           "{issue_pages}",
                           "{year}. \n &nbsp; &nbsp; \n",
                           .sep = ". ",
                           .na = character())) |>
    purrr::map_chr(\(x) gsub("Cole Brokamp", "**Cole Brokamp**", x = x, fixed = TRUE)) |>
    cat(sep = "\n\n")
}
```

```{r}
#| results: asis
cite_four(c("parikh-2024", "makkad-2024", "colegate-2024", "pennington-2022"))
```

# B. Positions, Scientific Appointments, and Honors

## Positions

|||
|:-----|:--------------------------|
|2022 – Present |	Associate Professor, Division of Biostatistics and Epidemiology, Cincinnati Children’s Hospital Medical Center, Department of Pediatrics, University of Cincinnati, College of Medicine |
|2017 – 2022 | Assistant Professor, Division of Biostatistics and Epidemiology, Cincinnati Children’s Hospital Medical Center, Department of Pediatrics, University of Cincinnati, College of Medicine|

## Scientific Appointments

|||
|:-----|:------------------|
| 2024 | NIH ZES1 LWJ-W (KA) |
| 2023 | NIH ZES1 BWD-D (HS) |
| 2023 | NIH ZES1 LWJ-W (K) |
| 2023 | NIH ZES1 LKB-K (P2) |
| 2023 | NIH ZRG1 MCST–B (14) |
| 2023 | NIH ZCTA1 TCRB-J (M2) |
| 2022 | NIH ZES1 WL-W (K) |
| 2022 | NIH ZES1 LWF-S (K9) |
| 2022 | NIH ZES1 LKB-S (KS) |
| 2019 | NIH SIEE study section, early career reviewer |

## Awards

|      |                                                         |
|:-----|:--------------------------------------------------------|
| 2020 | Cincinnati Children's Epidemiology and Biostatistics Top Publication |
| 2017 | Cincinnati Children's Epidemiology and Biostatistics Top Publication and Top Research Achievement |
| 2016 | Cincinnati Children's Arnold Strauss Fellowship Awardee |

# C. Contributions to Science

```{r}
#| child: contrib_science.Rmd
```
